\bf Model Visualization Techniques for a Social Network Model

### 2017-05-31 paper.Rnw
2.1 check

Network data is of frequent interest to researchers in a wide array of fields. There are technological networks, like power grids or the internet, information networks, such as citation networks or the World Wide Web, biological networks, e.g. neural networks, and social networks, just to name a few \citep{newman}. Each of these examples have one thing in common: their data structure. There are always units of observation, which we refer to throughout this paper as {\emph nodes}, and connections of some kind between those units, which we will call {\emph edges}. Networks might change over time, for example when new websites and hyperlinks are added on the World Wide Web, or when there are new people and relationships in a friendship network. Nodes and edges themselves also have inherent variables of interest, such as the  affiliation of authors in a co-authorship network, or the number of times two authors have collaborated.

The multiple layers of network data structures create unique struggles to network analysts. Some questions that researchers aim to answer can be: How does the strength of a connection between two nodes affect the overall structure of the network? Do node-level differences affect the formation or destruction of edges? Which views of the data are most informative for communicating effects and results of statistical analyses? These are, of course, just a few broad questions. In this paper we want to focus on the visual exploration of network data and models.

@@

Network visualization, also called network mapping, is a prominent subfield of network analysis. Visualizing network data is uniquely difficult because of the structure of the data itself.  Most, if not all, data visualizations rely on a well-defined axis inherited from the data. If data are numerical, histograms, scatterplots, or time series plots are straightforward to construct. If the data are categorical, bar charts and mosaic plots are available to to the researcher. If the data are spatial, there is a well-defined region in which to view information. Network data, however, are much less cut-and-dried.

There are two primary methods used to visualize networks: node-link diagrams and matrix visualization.
%\hh{As a toy example, let us assume that we have five nodes, $\{1,2,3,4,5\}$, connected by some edges: XXX list edges as $1 \mapto 2, 2 \mapto 4, ...$ }
We will use the toy data set shown below to demonstrate these two methods.

>>>>

Network data is of frequent interest to researchers in a wide array of fields. There are technological networks, like power grids or the internet, information networks, such as citation networks or the World Wide Web, biological networks, e.g. neural networks, and social networks, just to name a few \citep{newman}. Each of these examples have one thing in common: their data structure. There are always units of observation, which we refer to throughout this paper as \textit{nodes}, and connections of some kind between those units, which we will call \textit{edges}. Networks might change over time, for example when new websites and hyperlinks are added on the World Wide Web, or when there are new people and relationships in a friendship network. Nodes and edges themselves also have inherent variables of interest, e.g.\ the affiliation of authors in a co-authorship network, or the number of times two authors have collaborated.

The multiple layers of network data structures create unique struggles to network analysts. Some questions that researchers aim to answer are: How does the strength of a connection between two nodes affect the overall structure of the network? Do node-level differences affect the formation or destruction of edges? Which views of the data are most informative for communicating effects and results of statistical analyses? These are, of course, just a few broad questions. In this paper we want to focus on the visual exploration of network data and models.

@@

Network visualization, also called network mapping, is a prominent subfield of network analysis. Visualizing network data is uniquely difficult because of the structure of the data itself.  Most, if not all, data visualizations rely on well-defined axes inherited from the data. If variables are numerical, histograms, scatterplots, or time series plots are straightforward to construct. If the variables are categorical, bar charts and mosaic plots are available to to the researcher. If the data are spatial, there is a well-defined region in which to view information. Network data, however, are much less cut-and-dried.

There are two primary methods used to visualize networks: node-link diagrams and matrix visualization. XX INSERT REFS XX
%\hh{As a toy example, let us assume that we have five nodes, $\{1,2,3,4,5\}$, connected by some edges: XXX list edges as $1 \mapto 2, 2 \mapto 4, ...$ }
We will use the toy data set shown below to demonstrate these two methods.
